### 2019-06-23 papers/journal/bio.tex
Updated draft with the reviews contents

	\caption{Schematic of the VTS. Steps involved in vesicle transport between two compartments: a source and a target compartment are shown. 
	%
	The symbols used for different molecules involved in vesicle traffic are explained in the key. At the source compartment, transmembrane cargo proteins are sorted by cytosolic adaptor proteins. 
	%
	Here, different colours indicate different types of cargo and adaptor proteins. Coat proteins are recruited to the forming vesicle by adaptor proteins. 
	%
	Note here that a single type of coat protein can interact with multiple types of adaptor proteins. Subsequently, the vesicle is pinched off at its neck, for example by dynamin. 
	%
	Once the vesicle has left the source compartment, the coat and adaptor proteins fall off and the vesicle is recognized and bound by a tethering complex which is linked to the target compartment. 
	%
	At the target compartment, the tethered vesicle undergoes fusion, thereby releasing its contents}
    \label{fig:vts}
\end{figure}

\subsubsection{Vesicle budding} The process of vesicle budding involves sorting and packaging of cargo molecules, membrane deformation and budding of the vesicle from the source compartment (Fig.~\ref{fig:vts}).
%
Cargo sorting is performed by cytosolic adaptor proteins. 
Adaptors are recruited to the source compartment through interactions with the lipids that form the compartment's membrane, and interactions with molecular switches called Arf/Sar which signal the initiation of vesicle formation~\cite{paczkowski2015cargo}. 
%
Then these adaptors bind to cargo molecules and thereby sequester them for packaging. 
%
Different adaptor proteins act at different compartments, for example, vesicle formation at the ER requires the adaptor sec23/24, and the AP2 adaptor is used for packaging vesicles at the plasma membrane.
%

The next step is membrane deformation, which involves cytosolic coat proteins. 
%
Coat proteins are recruited to the forming vesicle through their interaction with adaptor proteins. 
%
These are naturally curved proteins, and their assembly on membranes leads to membrane deformation.
%
A single kind of coat protein can bind to multiple kinds of adaptors, thereby allowing the packaging of multiple types of cargo within the same vesicle. 
%
There are three major types of coat proteins: Clathrin, COP2, and COP1. These act on different compartments: the clathrin coat operates at multiple compartments, and can interact with multiple adaptors proteins, whereas the COP2 and COP1 coat are only involved in vesicle formation at a single compartment: the ER and the Golgi respectively~\cite{faini2013vesicle}.
%
Finally, transport vesicles bud out from the source compartment~\cite{cocucci2014dynamin}.
%
The vesicle is now ready for transport and subsequent fusion with a target compartment.

\subsubsection{Vesicle fusion} The process of vesicle fusion involves two steps recognition of the correct target compartment and fusion of the transport vesicle (Fig.~\ref{fig:vts}).

Target compartment recognition involves molecular switches called Rabs and tethering complexes. Distinct compartments of the cell are associated with distinct Rabs. For example, Rab5 is associated with early endosomes and Rab7 with late endosomes~\cite{rink2005rab}.  
%
Rabs are master regulators; in their active form, Rabs recruit many downstream proteins, including tethering complexes, fusion regulators, motor proteins, etc, to their compartment~\cite{muller2018molecular}.

Tethering complexes sequester vesicles to their target compartments by binding to the vesicle on one end and the target compartment on the other end, thereby bridging the two before fusion. 
%
They are also believed to function as chaperones for assembly of SNARE protein complexes, which enable vesicle fusion. 
%
A clear mechanism for the action of these tethers is missing, but evidence from experiments indicate that tethers bind to vesicles through molecular interactions with vesicle coat proteins, vesicle, associated Rabs, SNAREs and SNARE regulators. 
%
They can also sense membrane curvature (vesicles are highly curved) ~\cite{baker2016chaperoning}.

@@

\subsubsection{Molecular regulation} 
Fusion takes place only if the SNARE types involved in the vesicle and compartment are both in an active state.
%We assume that for fusion to occur, the pair of 
%
The activity of these SNAREs is dependent on the presence of other molecules on the vesicle or compartment, respectively.
%
In our abstract model, 
we create a hierarchy of variants for varying degrees of regulation of SNARE activity.
%we create a set of variations of different kind of molecular regulations.
%
Most generally, the activity state of a given SNARE can be a Boolean function of all the molecular types on a compartment or vesicle. 
%
We have also tested \cite{shukla2017discovering} a particularly simple regulation mechanism in which two SNAREs that can pair to drive fusion to inhibit one another; this is the \textit{pairing inhibition}. 
%
This is motivated by the idea that pairing must generate an inactive bi-molecular complex.
%

@@

%
%Properties of the VTS would be hindered by the same reason. 
%3-connected graphs and all possible variations of SNARE regulation rules. 
%
%The number of graphs of specified connectivity grows exponentially with the number of nodes: Table~\ref{tab:threec} shows how many 3-edge-connected graphs~\cite{a052448-oeis} exist (without parallel or self edges) as node number N increases.
\subsection{Graph connectivity is an interesting and accessible property of the VTS} 
%\textbf{Properties of a VTS that satisfies all cell-biological constraints:} 
\noindent Interactions between the molecules of the VTS together produce a functional vesicle transport network, in which molecules flow between intracellular compartments using specified paths.
%
The molecules of the VTS, their interactions, and modes of regulation have been worked out to a large extent through cell-biological experiments. 
%
But we do not know if this information is complete. In order to assess how completely we know the VTS, we need easily readable benchmarks.

One such benchmark is provided by our result about the connectivity of the VTS graph. Graph connectivity is defined as the minimum number of edges that need to be removed from an undirected graph to render it disconnected. For example, in a directed cyclic graph, every node has at least one incoming and one outgoing edge, at least 2 edges need to be removed in order to disconnect the graph. Therefore the underlying undirected graph is 2-connected. 
From our result, for a given set of biomolecular interactions, for a cell that is in a steady state, we expect the VTS graph to have a certain k-connectivity. When regulation is given by arbitrary Boolean rules, we find that VTS graphs must be 3-connected. And when we add the constraint of the specific form of regulatory interactions seen between VTS molecules, we expect vesicle transport graphs to be 2 strongly connected.

%\ankit{We need not specify Synthesis here. Only connectivity use next subsection to build this.}
%\somya{But this is the para where we explain why connectivity is interesting an biological property}
%\ankit{Yes; Both of our remark looks correct!}
The vesicle transport graphs available today for eukaryotic organisms are incomplete themselves. 
%
In this situation, we use our result as a tool to predict missing edges which satisfy the graph connectivity constraint. 
%
These predictions are intended to be used as guides for future experiments. 
%
A mismatch between our predictions and experiments would indicate that our current understanding of the VTS molecules is necessarily incomplete. 
%
Note that, on the other hand, if our predictions are experimentally confirmed, it does not imply that our understanding of the VTS is complete.\\
%
%\begin{table}[!t]
%	\caption{Table Caption}
%	\label{tab1}
%	\centering
%	{\setlength\tabcolsep{0.1pt}%
%		\begin{tabular}{ccccccccccccccc}
%			& $D_1$ & $D_2$ & $D_3$ & $D_4$ & $D_5$ & $D_6$ && & $D_1$ & $D_2$ & $D_3$ & $D_4$ & $D_5$ & $D_6$ \\
%			$D_1$ & & \cca{0} & \cca{0} & \cca{0} & \cca{2} & \cca{0} && $D_1$ && \cca{0} & \cca{0} & \cca{2} & \cca{2} & \cca{2} \\
%			$D_2$ & \cca{0} & & \cca{2} & \cca{0} & \cca{2} & \cca{0} && $D_2$ & \cca{0} &  & \cca{3} & \cca{0} & \cca{0} & \cca{2} \\
%			$D_3$ & \cca{7} & \cca{4} &  & \cca{3} & \cca{0} & \cca{4} && $D_3$ & \cca{0} & \cca{4} &  & \cca{4} & \cca{2} & \cca{0} \\
%			$D_4$ & \cca{3} & \cca{0} & \cca{7} &  & \cca{4} & \cca{0} && $D_4$ & \cca{0} & \cca{0} & \cca{5} &  & \cca{0} & \cca{0} \\
%			$D_5$ & \cca{3} & \cca{7} & \cca{7} & \cca{2} &  & \cca{4} && $D_5$ & \cca{2} & \cca{2} & \cca{0} & \cca{4} &  & \cca{4} \\
%			$D_6$ & \cca{2} & \cca{2} & \cca{7} & \cca{2} & \cca{6} &  && $D_6$ & \cca{2} & \cca{2} & \cca{3} & \cca{0} & \cca{4} & \\
%	\end{tabular}}
%\end{table}
%
\input{fig2}
%
\begin{example}
%
In Fig.~\ref{fig:M1}, we present a VTS that has 2 compartments and 18 molecules with its corresponding pairing matrix.
%
%Molecules are represented as $Q_{i}$'s or $R_{i}$'s to make a clear distinction between Q and R SNAREs.
%
In the VTS, labels are a set of molecule, where we show active molecules in red color.
%
The activity of the molecules on the node is controlled
by the presence of the other molecules (exact Boolean function is not shown). 
%
The activity of the molecules on an edge is determined by the corresponding pairing matrix.
%
Note that molecules $X$ and $Y$ do not take part in the fusion but determine the activity of molecules at the corresponding nodes.
%
Below the VTS, we show the pairing matrix.
%
Rows in the matrix correspond to the labels of edges, and columns correspond to the labels of nodes.
%
An entry 1 represents pairing between molecules and 0 represents no pairing.
%
Every molecule flows on a cycle, ensuring steady state.
%
This is a 4-connected graph.
\end{example}
%
%\subsection{Modeling and Symbolic Analysis of VTS: An Overview}
\label{subsec:graphmodel}
%
\subsection{Combinatorial problem and use of Formal methods}
\noindent The analysis of VTS is a difficult problem
because of the combinatorial scaling of possible traffic topologies and regulatory rules. 
%
%For example, we might want to check some conjecture of interest for all graphs of a certain structure. 
%
%If the analysis is done on a large number of graphs, the joined effect of large quantity of graphs and combinatorially many possible regulatory rules will be difficult to handle by any tool.
If the analysis is done on a large number of graphs, the joined effect of this with combinatorially many possible regulatory rules will be difficult to handle by any tool.
%
Precise analysis of the properties of the VTS would be hindered for the same reason.

>>>>

	\caption{(A) Schematic of the vesicle transport system. Steps involved in vesicle transport between
		two compartments: a source and a target compartment, are shown. The symbols used for different
		molecules involved in vesicle traffic are explained in the key. At the source compartment,
		transmembrane cargo proteins are sorted by cytosolic adaptor proteins. Here, different colours
		indicate different types of cargo and adaptor proteins. Coat proteins are recruited to the forming
		vesicle by adaptor proteins. Note here that a single type of coat protein can interact with multiple
		types of adaptor proteins. Subsequently, the vesicle is pinched off at its neck, for example by dynamin
		protein. Once the vesicle has left the source compartment, the coat and adaptor proteins fall off and
		the vesicle is recognized and bound by a tethering complex which is linked to the target compartment.
		At the target compartment, the tethered vesicle undergoes fusion, thereby releasing its contents. (B)
		SNARE regulation network. Here, the dark blue, light blue, green and red stripes represent Qa, Qb,
		Qc and R SNAREs respectively. These 4 SNAREs interact to form a SNARE complex. SNARE
		complex formation is regulated by SM proteins and Sec 17/18. SM proteins inhibit SNARE complex
		formation by inactivating Qa SNAREs. They also enhance SNARE complex formation by stabilizing
		intermediate structures, and by inhibiting premature SNARE complex resolution. Sec17/18 aid in
		SNARE complex resolution. (C) A schematic of the typic eukaryotic cell's VTS. Large circles
		represent compartments, and edges represent vesicle routes. Identities of compartments are written
		inside or beside them; ER = endoplasmic reticulum, Golgi = Golgi apparatus, PM = plasma
		membrane, EE = early endosome, LE = late endosome, Lys = lysosome. The two major vesicle routes;
		the secretory and the endocytic routes are in blue and orange, respectively. The routes in green
		represent vesicles that allow cross-talk between the secretory and the endocytic routes. }
    \label{fig:vts}
\end{figure}

\subsubsection{Vesicle budding} 
The process of vesicle budding involves sorting and packaging of cargo molecules, membrane deformation and budding of the vesicle from the source compartment (Fig.~\ref{fig:vts}). 
%
Cargo sorting is performed by cytosolic adaptor proteins. 
%
Adaptor proteins bind to cargo molecules on the source
compartment and thereby sequester them for packaging \cite{paczkowski2015cargo}. 
%
Next, cytosolic coat proteins are recruited to the forming vesicle through their interaction with adaptor proteins \cite{faini2013vesicle}. 
%
Coat proteins cause membrane deformation. 
%
Finally, transport vesicles bud out from the source
compartment \cite{cocucci2014dynamin}. 
%
The vesicle is now ready for transport and subsequent fusion with a target compartment.
%
%The process of vesicle budding involves sorting and packaging of cargo molecules, membrane deformation and budding of the vesicle from the source compartment (Fig.~\ref{fig:vts}).
%%
%Cargo sorting is performed by cytosolic adaptor proteins. 
%Adaptors are recruited to the source compartment through interactions with the lipids that form the compartment's membrane, and interactions with molecular switches called Arf/Sar which signal the initiation of vesicle formation~\cite{paczkowski2015cargo}. 
%%
%Then these adaptors bind to cargo molecules and thereby sequester them for packaging. 
%%
%Different adaptor proteins act at different compartments, for example, vesicle formation at the ER requires the adaptor sec23/24, and the AP2 adaptor is used for packaging vesicles at the plasma membrane.
%%
%
%The next step is membrane deformation, which involves cytosolic coat proteins. 
%%
%Coat proteins are recruited to the forming vesicle through their interaction with adaptor proteins. 
%%
%These are naturally curved proteins, and their assembly on membranes leads to membrane deformation.
%%
%A single kind of coat protein can bind to multiple kinds of adaptors, thereby allowing the packaging of multiple types of cargo within the same vesicle. 
%%
%There are three major types of coat proteins: Clathrin, COP2, and COP1. These act on different compartments: the clathrin coat operates at multiple compartments, and can interact with multiple adaptors proteins, whereas the COP2 and COP1 coat are only involved in vesicle formation at a single compartment: the ER and the Golgi respectively~\cite{faini2013vesicle}.
%%
%Finally, transport vesicles bud out from the source compartment~\cite{cocucci2014dynamin}.
%%
%The vesicle is now ready for transport and subsequent fusion with a target compartment.

\subsubsection{Vesicle fusion} 
The process of vesicle fusion involves two steps: recognition of the correct target compartment and fusion of the transport vesicle (Fig.~\ref{fig:vts}). 
%
Target compartment recognition involves molecular
switches called Rabs and tethering complexes \cite{rink2005rab}. 
%
Rabs are master regulators; in their active form, Rabs recruit many downstream proteins, including tethering complexes, fusion regulators, motor proteins, etc, to their compartment \cite{muller2018molecular}. 
%
Tethering complexes sequester vesicles to their target compartments by binding to the vesicle on one end and the target compartment on the other end, thereby bridging the two
before fusion \cite{baker2016chaperoning}.

@@

\subsubsection{Molecular regulation} 
Fusion takes place only if the SNARE types involved in the vesicle and compartment are both in an active state.
%We assume that for fusion to occur, the pair of 
%
The activity of these SNAREs is dependent on the presence of other molecules on the vesicle or compartment, respectively.
%
In our abstract model, 
we create a hierarchy of variants for varying degrees of regulation of SNARE activity.
%we create a set of variations of different kind of molecular regulations.
%
Most generally, the activity state of a given SNARE can be a Boolean function of all the molecular types on a compartment or vesicle. 
%
We have also tested \cite{shukla2017discovering} a particularly simple regulation mechanism in which two SNAREs that can pair to drive fusion to inhibit one another; this is the \textit{pairing inhibition}. 
%
This is motivated by the idea that pairing must generate an inactive bi-molecular complex.
%
Pairing inhibition can be encoded as a pairing matrix $P$, whose rows and columns represent the molecule types present in the VTS. 
%
$P(i,j)$ = 1 implies that molecule $i$ binds molecule $j$.
%
In our simple pairing inhibition scheme, if $P(i,j)$ = 1 and both molecules $i$ and $j$ are present on the same compartment, $i$ and $j$ are inactive, and therefore cannot cause fusion.

@@

%
%Properties of the VTS would be hindered by the same reason. 
%3-connected graphs and all possible variations of SNARE regulation rules. 
%
%The number of graphs of specified connectivity grows exponentially with the number of nodes: Table~\ref{tab:threec} shows how many 3-edge-connected graphs~\cite{a052448-oeis} exist (without parallel or self edges) as node number N increases.
\subsection{Graph connectivity is an interesting and accessible property of the VTS} 
%\textbf{Properties of a VTS that satisfies all cell-biological constraints:} 
%\noindent Interactions between the molecules of the VTS together produce a functional vesicle transport network, in which molecules flow between intracellular compartments using specified paths.
%%
%The molecules of the VTS, their interactions, and modes of regulation have been worked out to a large extent through cell-biological experiments. 
%%
%But we do not know if this information is complete. In order to assess how completely we know the VTS, we need easily readable benchmarks. 
%
%One such benchmark is provided by our result about the connectivity of the VTS graph. Graph connectivity is defined as the minimum number of edges that need to be removed from an undirected graph to render it disconnected. 
%\textbf{Properties of a VTS that satisfies all cell-biological constraints:} 
Suppose we are given a particular transport graph, a particular labeling of all the compartments and edges, a particular fusion pairing matrix, and a particular regulatory model. This information is then sufficient to check the following properties, which summarise the cell-biological constraints described above:
\begin{enumerate}
	\item We can determine which molecules are active on every compartment or vesicle.
	\item For every vesicle fusing to a compartment, we can determine whether there exists an active pair (one molecule on the vesicle, one on the compartment) which drives that fusion event.
	\item For every vesicle-compartment pair where the vesicle does not fuse to the compartment, we can verify that there is no pairing of active molecules on the
	vesicle and compartment that could drive their fusion.
	\item We can verify that every molecular type entering a compartment also leaves the compartment, and also that every molecular type entering a set of compartments also leaves that set. This is the steady state condition. In the biological literature this is often referred to as “homeostasis” and is a widespread and well-accepted assumption about cellular behaviour, at least over timescales of minutes to hours \cite{mani2016stacking}.
\end{enumerate}

The biological problem often boils down to such an analysis. A cell biologist might determine which molecules flow between which set of compartments, and biochemical experiments could be used to see how these molecules activate one another. We can then ask: is this a complete and consistent description? That is, do all the required properties listed above hold, given what the experimentalists have told us? It is often the case that biological data is missing. For example, only a few of the dozens of molecules involved in real VTSs have been mapped out. Therefore, it is extremely likely that the description provided by the cell biologist is incomplete. We can use our model to find out which properties have failed to hold, and thus prescribe new experiments in order to fill in the missing information.

Can we find a simple test to see whether any information is missing, given the experimental data? It has shown that graph k-connectedness furnishes precisely such a test \cite{shukla2017discovering}.
%
If the data provided by cell-biologists, suitably represented as a graph, does not have a certain degree of connectivity, this implies that some biological data has been missed. (The converse is not true: even if the required connectivity does hold, there might of course be more information missing.)

%The result about k-connectedness being a useful test of missing information \cite{shukla2017discovering} was obtained using SAT solvers for graphs up to a certain size, and a certain number of molecules. This was due to limitations in how we encoded the problem. Here we present a much more natural encoding that allows our result to be extended to graph sizes and molecule numbers that are typical of those found in real cells.

%For example, in a directed cyclic graph, every node has at least one incoming and one outgoing edge, at least 2 edges need to be removed in order to disconnect the graph. Therefore the underlying undirected graph is 2-connected. 
%From our result, for a given set of biomolecular interactions, for a cell that is in a steady state, we expect the VTS graph to have a certain k-connectivity. When regulation is given by arbitrary Boolean rules, we find that VTS graphs must be 3-connected. And when we add the constraint of the specific form of regulatory interactions seen between VTS molecules, we expect vesicle transport graphs to be 2 strongly connected.

%\ankit{We need not specify Synthesis here. Only connectivity use next subsection to build this.}
%\somya{But this is the para where we explain why connectivity is interesting an biological property}
%\ankit{Yes; Both of our remark looks correct!}
%The vesicle transport graphs available today for eukaryotic organisms are incomplete themselves. 
%%
%In this situation, we use our result as a tool to predict missing edges which satisfy the graph connectivity constraint. 
%%
%These predictions are intended to be used as guides for future experiments. 
%%
%A mismatch between our predictions and experiments would indicate that our current understanding of the VTS molecules is necessarily incomplete. 
%%
%Note that, on the other hand, if our predictions are experimentally confirmed, it does not imply that our understanding of the VTS is complete.\\
%%
%\begin{table}[!t]
%	\caption{Table Caption}
%	\label{tab1}
%	\centering
%	{\setlength\tabcolsep{0.1pt}%
%		\begin{tabular}{ccccccccccccccc}
%			& $D_1$ & $D_2$ & $D_3$ & $D_4$ & $D_5$ & $D_6$ && & $D_1$ & $D_2$ & $D_3$ & $D_4$ & $D_5$ & $D_6$ \\
%			$D_1$ & & \cca{0} & \cca{0} & \cca{0} & \cca{2} & \cca{0} && $D_1$ && \cca{0} & \cca{0} & \cca{2} & \cca{2} & \cca{2} \\
%			$D_2$ & \cca{0} & & \cca{2} & \cca{0} & \cca{2} & \cca{0} && $D_2$ & \cca{0} &  & \cca{3} & \cca{0} & \cca{0} & \cca{2} \\
%			$D_3$ & \cca{7} & \cca{4} &  & \cca{3} & \cca{0} & \cca{4} && $D_3$ & \cca{0} & \cca{4} &  & \cca{4} & \cca{2} & \cca{0} \\
%			$D_4$ & \cca{3} & \cca{0} & \cca{7} &  & \cca{4} & \cca{0} && $D_4$ & \cca{0} & \cca{0} & \cca{5} &  & \cca{0} & \cca{0} \\
%			$D_5$ & \cca{3} & \cca{7} & \cca{7} & \cca{2} &  & \cca{4} && $D_5$ & \cca{2} & \cca{2} & \cca{0} & \cca{4} &  & \cca{4} \\
%			$D_6$ & \cca{2} & \cca{2} & \cca{7} & \cca{2} & \cca{6} &  && $D_6$ & \cca{2} & \cca{2} & \cca{3} & \cca{0} & \cca{4} & \\
%	\end{tabular}}
%\end{table}
%
\input{fig2}
%
\begin{example}
%
In Fig.~\ref{fig:M1}, we present a VTS that has 2 compartments and 18 molecules with its corresponding pairing matrix.
%
%Molecules are represented as $Q_{i}$'s or $R_{i}$'s to make a clear distinction between Q and R SNAREs.
%
In the VTS, labels are a set of molecule, where we show active molecules in red color.
%
The activity of the molecules on the node is controlled
by the presence of the other molecules (exact Boolean function is not shown). 
%
The activity of the molecules on an edge is determined by the corresponding pairing matrix.
%
Note that molecules $X$ and $Y$ do not take part in the fusion but determine the activity of molecules at the corresponding nodes.
%
Below the VTS, we show the pairing matrix.
%
Rows in the matrix correspond to the labels of edges, and columns correspond to the labels of nodes.
%
An entry 1 represents pairing between molecules and 0 represents no pairing.
%
Every molecule flows on a cycle, ensuring steady state.
%
This is a 4-connected graph.
\end{example}
%
%\subsection{Modeling and Symbolic Analysis of VTS: An Overview}
\label{subsec:graphmodel}
%
\subsection{Combinatorial problem and use of Formal methods}
\noindent The analysis of VTS is a difficult problem
because of the combinatorial scaling of possible traffic topologies and regulatory rules. 
%
%For example, we might want to check some conjecture of interest for all graphs of a certain structure. 
%
%If the analysis is done on a large number of graphs, the joined effect of large quantity of graphs and combinatorially many possible regulatory rules will be difficult to handle by any tool.
If the analysis is done on a large number of graphs, the joined effect of this with combinatorially many possible regulatory rules will be difficult to handle by any tool.
%
Precise analysis of the properties of the VTS would be hindered for the same reason.

### 2019-06-23 papers/journal/conclusion.tex
Updated draft with the reviews contents

\noindent 
To conclude, we have established a connection between vesicle transport graph connectedness and underlying rules of SNARE pairing and regulation. 
%
The constraints implied by SNARE protein properties translates into
mathematically elegant properties of the transport graph, namely its connectivity.
%
Our approach demonstrates the power of SMT solvers in a {\em novel} application and the value of careful encoding of the problems into SMT queries. 
We manage to scale the tool up to the size that makes the tool biologically relevant.
%

>>>>

\noindent 
We demonstrate in our work how local regulatory interactions between molecules of the VTS, translate
into a global, observable properties of the VTS. 
%
Interactions between SNARE proteins and their
regulators, which in its simplest form can be encoded in a pairing matrix, constrain the topological
properties of the transport graph; all VTSs based on v-SNARE t-SNARE interactions must be 2-strongly connected.
% 
Additionally, we demonstrate how we can aid in predicting new vesicles given an incomplete VTS as input. 
%
Our approach demonstrates the power of SMT solvers in a novel application and the value of careful encoding of the problems into SMT queries. 
%
We manage to scale the tool up
to the size that makes the tool biologically relevant.
%To conclude, we have established a connection between vesicle transport graph connectedness and underlying rules of SNARE pairing and regulation. 
%%
%The constraints implied by SNARE protein properties translates into
%mathematically elegant properties of the transport graph, namely its connectivity.
%%
%Our approach demonstrates the power of SMT solvers in a {\em novel} application and the value of careful encoding of the problems into SMT queries. 
%We manage to scale the tool up to the size that makes the tool biologically relevant.
%
